---
title: "Parent-Child Visitation Portable Dashboard"
output:
 flexdashboard::flex_dashboard:
      theme: lumen
      keep_md: true
      self_contained: true
---
Days to Receipt {data-navmenu="Network-Level Stats"}
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(17," Days")
                   ,color = "#73A404",caption = "Until Visit is Received (from Creation Date)")
                   ``` 

### 1-Day Receipt Rate (from Creation Date)

                   ```{r}
                   gauge(67, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#73A404"))
                   ``` 

### Receipt Trends

           ```{r}
           library(dygraphs)

           `from Creation` <- measure_extract_time_series(df_file = "chron_long_created_to_received.rds"
           ,org_col = NA
           ,org_id = NA)

           dygraph(`from Creation`, main = "Metric Trends (Days to Receipt from Creation)") %>%
           dyOptions(colors = c("#73A404"), pointSize = 3, strokeWidth = 3,
           connectSeparatedPoints = TRUE) %>%
           dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
           dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
           ``` 

Days to Acceptance {data-navmenu="Network-Level Stats"}
=====================================
    Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(6.3," Days")
                   ,color = "#A43504",caption = "Until Visit is Accepted (from Receipt Date)")
                   ``` 

### 1-Day Acceptance Rate (from Receipt Date)

                   ```{r}
                   gauge(28, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#A43504"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(11.9," Days")
                   ,color = "#A27D11",caption = "Until Visit is Accepted (from Creation Date)")
                   ``` 

### 1-Day Acceptance Rate (from Creation Date)

                   ```{r}
                   gauge(12, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#A27D11"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Acceptance Trends

           ```{r}
           library(dygraphs)

           `from Receipt` <- measure_extract_time_series(df_file = "chron_long_received_to_assigned.rds"
           ,org_col = NA
           ,org_id = NA)

           `from Creation` <- measure_extract_time_series(df_file = "chron_long_created_to_assigned.rds"
           ,org_col = NA
           ,org_id = NA)

           performance_ts <- cbind(`from Receipt`
           ,`from Creation`)
           dygraph(performance_ts, main = "Metric Trends (Days to Acceptance)") %>%
           dyOptions(colors = c("#A43504", "#A27D11"), pointSize = 3, strokeWidth = 3,
           connectSeparatedPoints = TRUE) %>%
           dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
           dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
           ``` 

###

           ```{r}
           library(dygraphs)

           New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

           dygraph(New, main = "New Referrals (Simulated Data)") %>%
           dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
           ``` 

Days to Schedule {data-navmenu="Network-Level Stats"}
=====================================
    Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(16.9," Days")
                   ,color = "#0473A4",caption = "Until Visit is Scheduled (from Creation Date)")
                   ``` 

### 3-Day Scheduling Rate (from Creation Date)

                   ```{r}
                   gauge(45, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0473A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(11.4," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Receipt Date)")
                   ``` 

### 3-Day Scheduling Rate (from Receipt Date)

                   ```{r}
                   gauge(59, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Scheduling Trends

           ```{r}
           library(dygraphs)

           `from Receipt` <- measure_extract_time_series(df_file = "chron_long_received_to_agreed.rds"
                            ,org_col = NA
           ,org_id = NA)

           `from Creation` <- measure_extract_time_series(df_file = "chron_long_created_to_agreed.rds"
                            ,org_col = NA
           ,org_id = NA)

           performance_ts <- cbind(`from Receipt`
           ,`from Creation`)
           dygraph(performance_ts, main = "Metric Trends (Days to Schedule)") %>%
           dyOptions(colors = c("#0423A4", "#0473A4"), pointSize = 3, strokeWidth = 3,
           connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
           ``` 

###

           ```{r}
           library(dygraphs)

           New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

           dygraph(New, main = "New Referrals (Simulated Data)") %>%
           dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
           ``` 

Case Composition {data-navmenu="Trends and Demographics"}
=====================================
### This section of the portable dashboard is under development. Please see the **Provider-Level Scheduling Stats** for a prototype of this product.

Refferal Trends {data-navmenu="Trends and Demographics"}
=====================================
### This section of the portable dashboard is under development. Please see the **Provider-Level Scheduling Stats** for a prototype of this product.


 New Beginnings Visitation and Parent Education {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(0," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(100, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(4.4," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(88, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(44.3," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(9, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### New Beginnings Visitation and Parent Education

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =6)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =6)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =6)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Service Alternatives {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(6.5," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(100, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(7.9," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(67, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(49.1," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(7, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Service Alternatives

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =11)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =11)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =11)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Unite Family Services {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(3.2," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(100, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(3.8," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(97, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(46," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(13, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Unite Family Services

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =14)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =14)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =14)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Family Visitation Volunteers of America {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(11.5," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(69, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(6," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(83, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(45.5," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(7, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Family Visitation Volunteers of America

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =8)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =8)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =8)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Martin Luther King Jr. Family Outreach Center {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                    ```{r}
                    valueBox(
                    "Metric Unavailable"
                    ,color = "#0416A4",caption = "for Days Until Visit is Scheduled (from Acceptance Date)")
                    ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                    ```{r}
                    ``` 

###

                   ```{r}
                   valueBox(paste(13," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(0, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(26," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(0, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Martin Luther King Jr. Family Outreach Center

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =16)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =16)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =16)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 GMC Training Institute {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(4.5," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(100, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(15.3," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(44, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(55.3," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(0, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### GMC Training Institute

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =10)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =10)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =10)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 G&A, LLC {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(15.4," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(40, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(2," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(100, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(43.5," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(3, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### G&A, LLC

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =13)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =13)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =13)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Love My Child Family Services {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(4.4," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(100, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(8.1," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(60, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(45.7," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(7, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Love My Child Family Services

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =9)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =9)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =9)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Angela's Family Services {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(3," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(100, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(6.9," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(90, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(38.6," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(22, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Angela's Family Services

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =22)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =22)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =22)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 The Salvation Army Nurturing Center for Children & Families {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(3.8," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(100, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(3.8," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(98, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(41.4," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(13, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### The Salvation Army Nurturing Center for Children & Families

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =4)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =4)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =4)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Reunified Services {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(10," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(50, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(7.2," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(58, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(651.2," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(4, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Reunified Services

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =112)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =112)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =112)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 American Indian Community Center {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(12," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(0, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(20," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(0, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(27.5," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(6, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### American Indian Community Center

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =7)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =7)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =7)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Service Alternatives - Spokane {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(13.3," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(33, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(9.1," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(43, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(46.6," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(10, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Service Alternatives - Spokane

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =161)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =161)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =161)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 Fulcrum Institute, DRC {data-orientation=rows, data-navmenu="Provider-Level Scheduling Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(15.8," Days")
                   ,color = "#0416A4",caption = "Until Visit is Scheduled (from Acceptance Date)")
                   ``` 

### 3-Day Scheduling Rate (from Acceptance Date)

                   ```{r}
                   gauge(19, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#0416A4"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(8.9," Days")
                   ,color = "#771086",caption = "for Days Until Visit is Expected to Occur (from Acceptance Date)")
                   ``` 

### 7-Day Expectation Rate (from Acceptance Date)

                   ```{r}
                   gauge(50, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#771086"))
                   ``` 

###

                   ```{r}
                   valueBox(paste(233.9," Days")
                   ,color = "#FC4F1E",caption = "for Days Until Visit is In-Progress (from Acceptance Date)")
                   ``` 



### 7-Day In-Progress Rate (from Acceptance Date)

                   ```{r}
                   gauge(8, min = 0, max = 100, symbol = "%"
                   ,gaugeSectors(colors = "#FC4F1E"))
                   ``` 

Row {data-height=400} 
-------------------------------------

### Fulcrum Institute, DRC

               ```{r}
library(dygraphs)

  Inprogress <- measure_extract_time_series(df_file = "chron_long_assigned_to_inprogress.rds"
                              ,org_col = "id_provider_dim_pcv"
               ,org_id =3)
  Schedule <- measure_extract_time_series(df_file = "chron_long_assigned_to_scheduled.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =3)
  Expected <- measure_extract_time_series(df_file = "chron_long_assigned_to_agreed.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =3)
               performance_ts <- cbind(Schedule
               ,Expected
               ,Inprogress)
  dygraph(performance_ts, main = "Metric Trends") %>%
               dyOptions(colors = c("#0416A4", "#771086", "#FC4F1E"), pointSize = 3, strokeWidth = 3,
connectSeparatedPoints = TRUE) %>%
dyEvent("2017-09-20", "Timeline Release", labelLoc = "top") %>%
dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

###

               ```{r}
library(dygraphs)

               New <- ts(rnorm(8, 15, 2), start = c(2016, 10), end = c(2017, 10), frequency = 12)

  dygraph(New, main = "New Referrals (Simulated Data)") %>%
    dyOptions(colors = c("#B58900"), pointSize = 3, strokeWidth = 3)
               ``` 

 New Beginnings Visitation and Parent Education {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(26,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(0,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### New Beginnings Visitation and Parent Education

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =6)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =6)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Service Alternatives {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(17,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(12,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Service Alternatives

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =11)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =11)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Unite Family Services {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(20,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(5,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Unite Family Services

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =14)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =14)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Family Visitation Volunteers of America {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(16,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(6,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Family Visitation Volunteers of America

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =8)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =8)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Martin Luther King Jr. Family Outreach Center {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(9,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(100,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Martin Luther King Jr. Family Outreach Center

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =16)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =16)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 GMC Training Institute {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(46,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(0,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### GMC Training Institute

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =10)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =10)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 G&A, LLC {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(27,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(5,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### G&A, LLC

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =13)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =13)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Love My Child Family Services {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(21,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(1,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Love My Child Family Services

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =9)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =9)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Angela's Family Services {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(18,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(17,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Angela's Family Services

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =22)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =22)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 The Salvation Army Nurturing Center for Children & Families {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(24,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(2,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### The Salvation Army Nurturing Center for Children & Families

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =4)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =4)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Reunified Services {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(15,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(14,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Reunified Services

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =112)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =112)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 American Indian Community Center {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(17,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(0,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### American Indian Community Center

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =7)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =7)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Service Alternatives - Spokane {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(22,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(5,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Service Alternatives - Spokane

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =161)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =161)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 



 Fulcrum Institute, DRC {data-orientation=rows, data-navmenu="Provider-Level Report Stats"} 
=====================================
Row {data-height=600, data-width=300} 
-------------------------------------

###

                   ```{r}
                   valueBox(paste(14,"%")
                   ,color = "#FC4A1A",caption = "24-Hour Cancellation Rate")
                   ``` 

###

                   ```{r}
                   valueBox(paste(9,"%")
                   ,color = "#F7B733",caption = "Among 24-Hour Cancellations, Rate of Provider Cause")
                   ``` 

Row {data-height=400} 
-------------------------------------

### Fulcrum Institute, DRC

               ```{r}
               library(dygraphs)
               `Provider Cancels` <- measure_extract_time_series(df_file = "prop_long_missed_visit.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =3)*100

               Cancels <- measure_extract_time_series(df_file = "prop_long_missed_visit_by_pvd.rds"
               ,org_col = "id_provider_dim_pcv"
               ,org_id =3)*100

           performance_ts <- cbind(Cancels
               ,`Provider Cancels`)

               dygraph(performance_ts, main = "Metric Trends (24-Hour Cancellation Rates)") %>%
               dyOptions(colors = c("#FC4A1A", "#F7B733"), pointSize = 3, strokeWidth = 3,
               connectSeparatedPoints = TRUE) %>%
               dyLegend(show = "onmouseover", hideOnMouseOut = TRUE, width = 400)
               ``` 

